\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-06-06 paper/ms.tex
Random work

\subsection{An example mixture model}
Consider a sampling distribution
for data $D=\{D_1, D_2, ..., D_n\}$ which is a mixture of $N$ gaussians
with means $\{\mu_j\}$, standard deviations $\{\sigma_j\}$, and
mixture weights $\{w_j\}$. The likelihood for the $i$th data point is
\begin{align}
p(D_i | N, \{\mu_j\}, \{\sigma_j\}, \{w_j\}) &=
\sum_{j=1}^N \frac{w_j}{\sigma_j\sqrt{2\pi}}
\exp\left[-\frac{1}{2\sigma_j^2}\left(D_i - \mu_j\right)^2\right].
\end{align}
Colloquially, one might say the data were 'drawn from' a mixture of
$N$ normal distributions, and we want to infer $N$ along with the
properties of those normal distributions.

@@

The \code{RJObject} constructor definition is:
\begin{CodeChunk}
\begin{CodeInput}
RJObject(int num_dimensions, int max_num_components, bool fixed,
         const ConditionalPrior& conditional_prior,
         PriorType prior_type=PriorType::uniform);
\end{CodeInput}
\end{CodeChunk}

>>>>

\subsection{An example mixture model}
Consider a sampling distribution
for data $D=\{D_1, D_2, ..., D_n\}$ which is a mixture of $N$ gaussians
with means $\{\mu_j\}$, standard deviations $\{\sigma_j\}$, and
mixture weights $\{w_j\}$. The likelihood for the $i$th data point is
\begin{align}
p\left(D_i | N, \{\mu_j\}, \{\sigma_j\}, \{w_j\}\right) &=
\sum_{j=1}^N \frac{w_j}{\sigma_j\sqrt{2\pi}}
\exp\left[-\frac{1}{2\sigma_j^2}\left(D_i - \mu_j\right)^2\right].
\end{align}
Colloquially, one might say the data were `drawn from' a mixture of
$N$ normal distributions, and we want to infer $N$ along with the
properties of those normal distributions.

@@

The \code{RJObject} constructor definition is:
\begin{CodeChunk}
\begin{CodeInput}
RJObject(int num_dimensions, int max_num_components, bool fixed,
         const ConditionalPrior& conditional_prior,
         PriorType prior_type=PriorType::uniform);
\end{CodeInput}
\end{CodeChunk}
where \code{num\_dimensions} is the number of parameters needed to
specify a single component (three in this example),
...
